After three and a half years as a PhD student, I would like to thank a number of people who have supported me on this journey. First, I would like to thank my main supervisor, Odd Erik Garcia.  In addition to his guidance and support, Odd Erik also gave me the opportunity to participate at summer schools at CCFE and MIT, visit DTU for two weeks during my first year and spend a whole year at CCFE. Visiting different research facilities and meeting many gifted scientists was one of the highlights during this time. 

I would also like to thank Fulvio Militello for hosting me at CCFE and proofreading parts of this thesis. Our weekly catch-ups in the last year and a half were extremely insightful and productive. I am grateful to him reserving time for me even though I am not directly supervised by him.

I am very grateful for being part of such friendly and supportive research groups. These include Audun Theodorsen, Ralph Kube, Juan Manuel Losada and Magdalena Korzeniowska at UiT. From CCFE these include John Omotani, Tom Nicholas, Fabio Riva, Sarah Newton and Nick Walkden as well as Matthias Wiesenberger at DTU. Further thanks go to my office mates, Patrick Stoll, Sindre Fritzner, Tuomas Heiskanen, Tom Farley, Daljeet Singh Gahle, Enrique Miralles and Joe Allcock. Raheesty Nishta Nem deserves my gratitude for proof-reading my thesis and giving me valuable comments. I am also grateful to the University of Tromsø – The Arctic University of Norway for funding my PhD. 

On a less academic note, I would like to thank my landlord in Oxford, Michael Butcher, for letting Sajidah and me stay in his flat during the UK-wide lockdown due to the COVID-19 pandemic. Being able to stay together with Sajidah made this challenging time much easier. Thanks also to my friends in Tromsø and Oxford, I have always been looking forward to spending time with you during band practice and other occasions.

Vielen Dank an meine Familie für eure Unterstützung und euer Verständnis für die örtliche Distanz. Auch wenn ich euch pandemiebedingt schon lange nicht mehr persönlich sehen konnte, bleibt ihr in meinem Herzen.

Finally, I would like to thank Sajidah for her patience, laughter and support. This PhD would not have been as joyful without you.